Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-10 proposal/proposal.tex
Updated Web Application section

\subsection{Web Application}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx group already has some protocols in place for collecting and displaying the data from the Magnetometor Fios, we will allow their group to continue the development on that part, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

\subsubsection{HTTP Interface}
The Raspberry Pi base station will need some way to communicate its data with the web application/MySQL database. The simplest way to meet this need is to create an HTTP interface on the server. We will need this interface to handle requests from the front end of the web application anyway, and so it makes sense to also allow the base station to communicate with our server through HTTP requests. We will create a RESTful HTTP interface that corresponds closely to the database schema and the front-end of the webpage, and the base station will send all its data to the application via the same interface. For example, if an image of a license plate is detected, the base station would send an HTTP POST request to http://acmxlabs.org/parking/license_image (actual urls may change when we start designing the interface), and the server would receive the request and send the image to the ALPR software, as described in section 2.5. When the web application needs to get the data associated with a license plate, it will send an HTTP GET request to http://acmxlabs.org/parking/license_plates/123ABC.

\subsubsection{Viewing License Plate Data}
As mentioned in section 2.5, the license plate imnages will be translated from an image into a string of plain text, and stored in the MySQL database on the ACMx server. One of the main functions of the web interface will be the display of this data to administrators. The page that displays the license plate data will have a simple interface which will allow administrators to filter the data by date/time, lot, and license plate number. For example, an administrator should be able to type in a specific license plate number and see all the dates/times that plate has been seen, and in which lot. Alternatively, an admin will be able to enter a date range and lot(s) and see all the license plates that entered/exited the lot(s) during that date range. For now we are only interested in a proof-of-concept type interface that shows that we have the capability to display the collected plate data in a useful format; in the future it could be incredibly useful to cross reference our data with the campus parking department's database to check if a car has entered a lot without a permit.

>>>>

\subsection{Web Application}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx group already has some protocols in place for collecting and displaying the data from the magnetometer Fios, we will allow their group to continue the development on that part, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

\subsubsection{HTTP Interface}
The Raspberry Pi base station will need some way to communicate its data with the web application/MySQL database. The simplest way to meet this need is to create an HTTP interface on the server. We will need this interface to handle requests from the front end of the web application anyway, and so it makes sense to also allow the base station to communicate with our server through HTTP requests. We will create a REST-ful HTTP interface that corresponds closely to the database schema and the front-end of the webpage, and the base station will send all its data to the application via the same interface. For example, if an image of a license plate is detected, the base station would send an HTTP POST request to 'acmxlabs.org/parking/licenseImage' (actual urls may change when we start designing the interface), and the server would receive the request and send the image to the ALPR software, as described in section 2.5. When the web application needs to get the data associated with a license plate, it will send an HTTP GET request to 'acmxlabs.org/parking/licensePlate/123ABC'.

\subsubsection{Viewing License Plate Data}
As mentioned in section 2.5, the license plate images will be translated from an image into a string of plain text, and stored in the MySQL database on the ACMx server. One of the main functions of the web interface will be the display of this data to administrators. The page that displays the license plate data will have a simple interface which will allow administrators to filter the data by date/time, lot, and license plate number. For example, an administrator should be able to type in a specific license plate number and see all the dates/times that plate has been seen, and in which lot. Alternatively, an admin will be able to enter a date range and lot(s) and see all the license plates that entered/exited the lot(s) during that date range. For now we are only interested in a proof-of-concept type interface that shows that we have the capability to display the collected plate data in a useful format; in the future it could be incredibly useful to cross reference our data with the campus parking department's database to check if a car has entered a lot without a permit.
